---
title: "NFHS Data Analysis"
author: "Varun"
date: "`r Sys.Date()`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Documentation

The National Family Health Survey (NFHS) is a large-scale, 
            multi-round survey conducted in a representative sample of households throughout India. 
            Three rounds of the survey have been conducted since the first survey in 1992-93.
            This dashboard uses district factsheet data of the latest NFHS-5 data held in 2019-2020. 
            The dashboard gives state wise filtering and display bar chart of health indicators
            district ise. This will help in easy searching of the Data to 
            find district level indicators.
            See the Link for data source:
            <https://www.kaggle.com/datasets/kmldas/india-national-family-health-survey-nfhs?resource=download>.


## Description of Shiny App.

- Link for the shiny app . See <https://varunmr.shinyapps.io/NFHS/>
- Select the State then indicator you are interested.
- A barplot output with district values will be shown. It filters the state and select indicator column at server.

## Slide with R Output

```{r include=FALSE}
library(readr)
library(tidyverse)
```


```{r , echo=TRUE}
nfhs <- read_csv("D:/Data Science/R/John Hopkins/Data Products/Shiny/nfhs/data/NFHS_5_India_Districts_Factsheet_Data.csv")
 nfhs1<-nfhs%>%
           filter(`State/UT`=="Bihar")%>%select(`Men age 15 years and above who consume alcohol (%)`,1:2)
        ggplot(data=nfhs1,aes(x=reorder(`District Names`,`Men age 15 years and above who consume alcohol (%)`),y=`Men age 15 years and above who consume alcohol (%)`,fill=`District Names`))+
            geom_bar(stat = "identity",show.legend = FALSE)+
            geom_text(nfhs1,mapping=aes(label=`Men age 15 years and above who consume alcohol (%)`))+
            coord_flip()+
            labs(x="District Names",y="Men age 15 years and above who consume alcohol (%)")+
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
                                                             panel.background = element_blank(),axis.text.x = element_blank(),
                  axis.ticks.x = element_blank(),axis.text = element_text(face="bold"))
```

## Conclusion

The app really helps to quickly see district indicators without going through district factsheet pdf of every district.
